### 2018-08-30 scripts/01-datasets/README.Rmd
update readmes with github_markdown_nested format
rerender readmes using knit_nest

The datasets are split in real datasets and synthetic datasets. The real datasets are downloaded and preprocessed first, and characteristics from these datasets (such as the number of cells and genes, library sizes, dropout probabilities, ...) are used to generate synthetic datasets. Finally, these dataset are uploaded to zenodo.

@@

```{r results = 'asis'}
knit_child_readme("01-real")
```

```{r results = 'asis'}
knit_child_readme("02-synthetic")
```

```{r results = 'asis'}
knit_child_readme("05-dataset_characterisation")
```

>>>>

The datasets are split in real datasets and synthetic datasets. The real datasets are downloaded and preprocessed first, and characteristics from these datasets (such as the number of cells and genes, library sizes, dropout probabilities, ...) are used to generate synthetic datasets. The datasets are then characterised, after which they are uploaded to Zenodo.

@@

```{r results = 'asis'}
knit_nest("01-real")
```

```{r results = 'asis'}
knit_nest("02-synthetic")
```

```{r results = 'asis'}
knit_nest("04-dataset_characterisation")
```

### 2018-08-30 scripts/02-metrics/README.Rmd
metric characterisation -> metrics
update readmes with github_markdown_nested format
rerender readmes using knit_nest

---
output: 
  github_document:
    pandoc_args: --atx-headers
---

# Metric characterisation and testing

@@

```{r, results = "asis"}
knit_child_readme("01-individual_metrics")
```

```{r, results = "asis"}
knit_child_readme("02-metric_conformity")
```

>>>>

---
output: dynbenchmark::github_markdown_nested
---

# Metrics for comparing two trajectories

@@

```{r, results = "asis"}
knit_nest("01-metric_characterisation")
```

```{r, results = "asis"}
knit_nest("02-metric_conformity")
```
